PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-02-24 qfenv_paper/qf_environment.tex
updated figures

\subsection{Galaxy Sample} \label{sec:target} 
In this seciton we will define the galaxy sample we use for our SMFs and QFs.
The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} (listed in its Table 1).
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 1.0$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift 
failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation 1 in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

@@

\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We classify the galaxies from the target sample, defined in the last section, using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa}.
For a detailed description of the classification scheme, we refer readers to Section 3.2 in \cite{Moustakas:2013aa}.

@@

\begin{table*} %Will contain much more information on environments. 
  \caption{Subsample}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
  Survey    &Redshift ($z$) &Environment    &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
            &               &Mid            &3614                       &4438                           \\
            &               &Low            &5419                       &8927                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
            &               &Mid            &177                    &403                          \\
            &               &Low            &768                    &2516                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
            &               &Mid            &195                       &405                           \\
            &               &Low            &871                       &2385                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
            &               &Mid            &186                       &327                           \\
            &               &Low            &833                       &1847                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
            &               &Mid            &94                       &163                           \\
            &               &Low            &373                       &810                           \\
            &               &               &                       &                           \\ \hline
  \multicolumn{5}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}

@@

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
cumulative number density absolute magnitude cut off. 
\begin{table*} %Will contain much more information on environments. 
  \caption{Fixed Cylindrical Aperture Dimensions}
  \label{tab:aperture}
  \begin{center}
    \leavevmode
    \begin{tabular}{llllll} \hline \hline              
  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
  \multicolumn{6}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}
The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
We restrict the PRIMUS EDP galaxies within the redshift range $0.2-1.0$ and divide them into redshift bins of width $\Delta z = 0.2$. 
For each of these redshift bins, we impose separate absolute magnitude ($M_{g,\rm{lim}}$) limits such 
that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
number density of the highest redshift bin with an empirically determined limit. 
First, to determine the highest redshift bin ($0.8-1.0$) limit we look at the $M_{g}$ distribution with bin size
$\Delta M_{g} = 0.25$ and select $M_{g,\rm{lim}}$ to be the $M_{g}$ value near the peak of the 
distribution where number density of the bins with fainter objects (greater $M_{g}$ value) are smaller
than the number density of the bin at $M_{g, \rm{lim}}$. 
We find this $M_{g, \rm{lim}}( 0.8 < z < 1.0)$ to be, conservatively, $M_{g} = -20.75$. 
With this value we then calculate the rest of the $M_{g, \rm{lim}}$s by finding the
$M_{g}$ value where the cumulative number density ordered by absolute magnitude of the redshift bins 
equals that of the the highest redshift bin at $M_{g, \rm{lim}}( 0.8 < z < 1.0)$. 
Note that when calculating the number densities, the number of galaxies takes into account the 
statistical weights (described in Section \ref{sec:primus} and \ref{sec:sdss}).

For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
we do not use the parent sample of the data due to 
the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
to the redshift range of $0.01-0.2$ in \cite{Moustakas:20133aa}.
This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
galaxies at $z \sim 0.01$. 
In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
$M_{g}$ versus redshift distribution. 
The same fixed cumulative number density method is used on this SDSS EDP. 
By using a fixed cumulative number density method of 
Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies. 
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:targetEDP}
        \epsscale{1.0}
        \plotone{absmag_redshift_target_EDP_sdss00375-0145_primus02-10.png}
        \caption{Absolute magnitude $M_{g}$ vs. redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
    \end{center}
\end{figure*}

@@

\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edge effects of the survey.
For the target galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. 
In this case, the $n_{env}$ will only reflect the galaxies which lie in the fraction of the aperture contained within the survey geometry.

@@

\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{smf_cylr1h50_thresh80_PRIMUS_nbin6_SDSS_nbin2_smf_massbin03_jackknife.png}
        \caption{Stellar mass functions and quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}
Our primary interest in the SMFs is to investigate the evolution of the quiescent fraction in different density environments over our redshift range. 
Hence, we first divide the target galaxy sample into quiescent and star-forming target samples using the classification scheme from Section \ref{sec:sfq}.
Both the quiescent and star-forming target samples are then divided into "high-environment","mid-environment", and "low-environment" based on their environment classification described in 
Section \ref{sec:environment}.
We use the five redshift bins described in \ref{target} to get a total of $30$ subsamples that are classified based on star-forming/quiescent, environment, and redshift.
For each of these subsamples, we calculate the SMFs and their errors.

@@

Since the SDSS-{\em GALEX} data are contained in one field, we first divide the field into a $30 \times 20$ rectangular grid and then only keep the sectors with at least $100$ galaxies in them. 
Then we use the same method as above to compute the uncertainties through the jack knife technique. 
The panels in the top two rows of Figure \ref{fig:smf} show the SMFs with uncertainties for all $30$ subsamples using aperture with dimensions $R_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.

%Multiple apertures Additionally, we employ multiple apertures, as listed in Table \ref{tab:aperture}, since we are interested in probing the density environment at various scales. 
%Each aperture size will result in a different environment classification; so, $18$ SMFs are generated separately for every aperture we employ.

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr1h50_PRIMUS_nbin6_SDSS_nbin2_z00-10_slope-yint-err-fit_mass_100-115_105fidmass_01massbin.png}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for low (triangle), mid (square) and high (circle) environments in redshift bins: $0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$. Comparing these linear fit values in the redshift range for the different environment densities suggest that the change in QFs is indepdent of environment density.}
    \end{center}
\end{figure}

@@

\section{Appendix}
\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{smf_cylr2h50_thresh75_PRIMUS_nbin20_SDSS_nbin5_006_0145_smf_massbin03_jackknife.png}
        \caption{SMF and QF for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr2h50_PRIMUS_nbin20_SDSS_nbin5_z00-10_slope-yint-err-fit_mass_100-110_105fidmass_01massbin.png}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}

\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{smf_cylr1h25_thresh80_PRIMUS_nbin20_02_08_smf_massbin03_jackknife.png}
        \caption{SMF and QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{QFfit_cylr1h25_PRIMUS_z02-08_slope-yint-err-fit_mass_100-115_105fidmass_03massbin}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}
\end{document}

\end{document}

>>>>

\subsection{Galaxy Sample} \label{sec:target} 
\begin{table*} %Will contain much more information on environments. 
  \caption{Subsample}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
  Survey    &Redshift ($z$) &Environment    &Quiescent $N_{\rm{g}}$ &Star-forming $N_{\rm{g}}$  \\ \hline 
  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
            &               &Mid            &3614                       &4438                           \\
            &               &Low            &5419                       &8927                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
            &               &Mid            &177                    &403                          \\
            &               &Low            &768                    &2516                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
            &               &Mid            &195                       &405                           \\
            &               &Low            &871                       &2385                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
            &               &Mid            &186                       &327                           \\
            &               &Low            &833                       &1847                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
            &               &Mid            &94                       &163                           \\
            &               &Low            &373                       &810                           \\
            &               &               &                       &                           \\ \hline
  \multicolumn{5}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}
In this seciton we will define the galaxy sample we use for our SMFs and QFs.
The population at intermediate redshift is derived from the PRIMUS data and the population at low redshift is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data, \cite{Coil:2011aa}, and then we impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} (listed in its Table 1).
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 1.0$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift 
failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation 1 in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:targetEDP}
        \epsscale{1.0}
        \plotone{fig_EDP_absmag_redshift.png}
        \caption{Absolute magnitude $M_{r}$ vs. redshift for the target galaxy population (black) with the Environment Defining Population (red) plotted on top. Both samples are divided into redshift bins:$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. The target galaxy population is stellar mass complete (Section \ref{sec:target} while the EDP is volume limited through $M_{g}$ limits (Section \ref{sec:environment}).}
    \end{center}
\end{figure*}
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We classify the galaxies from the target sample, defined in the last section, using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa}.
For a detailed description of the classification scheme, we refer readers to Section 3.2 in \cite{Moustakas:2013aa}.

@@

@@

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
cumulative number density absolute magnitude cut off.

The EDP for the PRIMUS sample is derived from the same parent sample as the target galaxies. 
We restrict the PRIMUS EDP galaxies within the redshift range $0.2-1.0$ and divide them into redshift bins of width $\Delta z = 0.2$. 
For each of these redshift bins, we impose separate absolute magnitude ($M_{g,\rm{lim}}$) limits such 
that the cumulative number density of the sample ordered by $M_{g}$ is equal to the cumulative 
number density of the highest redshift bin with an empirically determined limit. 
First, to determine the highest redshift bin ($0.8-1.0$) limit we look at the $M_{g}$ distribution with bin size
$\Delta M_{g} = 0.25$ and select $M_{g,\rm{lim}}$ to be the $M_{g}$ value near the peak of the 
distribution where number density of the bins with fainter objects (greater $M_{g}$ value) are smaller
than the number density of the bin at $M_{g, \rm{lim}}$. 
We find this $M_{g, \rm{lim}}( 0.8 < z < 1.0)$ to be, conservatively, $M_{g} = -20.75$. 
With this value we then calculate the rest of the $M_{g, \rm{lim}}$s by finding the
$M_{g}$ value where the cumulative number density ordered by absolute magnitude of the redshift bins 
equals that of the the highest redshift bin at $M_{g, \rm{lim}}( 0.8 < z < 1.0)$. 
Note that when calculating the number densities, the number of galaxies takes into account the 
statistical weights (described in Section \ref{sec:primus} and \ref{sec:sdss}).

For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
we do not use the parent sample of the data due to 
the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
to the redshift range of $0.01-0.2$ in \cite{Moustakas:20133aa}.
This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
galaxies at $z \sim 0.01$. 
In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
$M_{g}$ versus redshift distribution. 
The same fixed cumulative number density method is used on this SDSS EDP. 
By using a fixed cumulative number density method of 
Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_smf_cylr2h25_thresh75_bin0_25.png}
        \caption{Stellar mass functions for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}
\subsection{Edge Effects} \label{sec:edgeeffect}
One of the challenges in obtaining the galaxy environment using a fixed aperture method is accounting for the edge effects of the survey.
For the target galaxies located near the edge of the survey, part of the fixed aperture encompassing it will lie outside the survey regions. 
In this case, the $n_{env}$ will only reflect the galaxies which lie in the fraction of the aperture contained within the survey geometry.

@@

\subsection{Stellar Mass Function} \label{sec:smf_const}
Our primary interest in the SMFs is to investigate the evolution of the quiescent fraction in different density environments over our redshift range. 
Hence, we first divide the target galaxy sample into quiescent and star-forming target samples using the classification scheme from Section \ref{sec:sfq}.
Both the quiescent and star-forming target samples are then divided into "high-environment","mid-environment", and "low-environment" based on their environment classification described in 
Section \ref{sec:environment}.
We use the five redshift bins described in \ref{target} to get a total of $30$ subsamples that are classified based on star-forming/quiescent, environment, and redshift.
For each of these subsamples, we calculate the SMFs and their errors.

@@

Since the SDSS-{\em GALEX} data are contained in one field, we first divide the field into a $30 \times 20$ rectangular grid and then only keep the sectors with at least $100$ galaxies in them. 
Then we use the same method as above to compute the uncertainties through the jack knife technique. 
The panels in the top two rows of Figure \ref{fig:smf} show the SMFs with uncertainties for all $30$ subsamples using aperture with dimensions $R_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.  
%Multiple apertures Additionally, we employ multiple apertures, as listed in Table \ref{tab:aperture}, since we are interested in probing the density environment at various scales. 
%Each aperture size will result in a different environment classification; so, $18$ SMFs are generated separately for every aperture we employ. 
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_qf_cylr2h25_thresh75_bin0_25.png}
        \caption{Quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.eps}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for low (triangle), mid (square) and high (circle) environments in redshift bins: $0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$. Comparing these linear fit values in the redshift range for the different environment densities suggest that the change in QFs is indepdent of environment density.}
    \end{center}
\end{figure}

@@

\section{Appendix}
\begin{table*} %Will contain much more information on environments. 
  \caption{Fixed Cylindrical Aperture Dimensions}
  \label{tab:aperture}
  \begin{center}
    \leavevmode
    \begin{tabular}{llllll} \hline \hline              
  Radius (Mpc)          &Height (Mpc)      &$n_{bin}$   &Edgecut &High Env Threshold (galaxies) &Low Env Threshold (galaxies) \\ \hline 
  1.0 &50 &6 & 80\% & 1.5 & 0.0          \\
  2.0 &50 &6 & 75\% & 4.0 & 0.0          \\ \hline
  \multicolumn{6}{l}{}                                             \\       
    \end{tabular}
  \end{center}
\end{table*}
\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_smf_cylr1h25_thresh80_bin0_25.png}
        \caption{SMF and QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.eps}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}
\end{document}
